%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[oneside,12pt]{book}
\usepackage[left=2cm,top=1cm,right=3cm,nofoot]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{a4paper}                   % ... or a4paper or a5paper or 
\usepackage{tabularx}



\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}
%\usepackage[english]{babel}
\usepackage{listings}
\usepackage{graphicx}
\usepackage[linktocpage]{hyperref}

\newcommand\don[5]{
\textbf{#1} \\
#2
\begin{itemize}
\item{ \textbf{Roll}: #3}
\item{ \textbf{Cost}: #4}
\item{ \textbf{Page}: #5}
\end{itemize}
\vspace{0.5cm}
}


\title{Roaming in the Wood}
\author{Renaud "Le Sage" Guezennec}
\date{}

%\let\origdescription\description
%\renewenvironment{description}{
%  \setlength{\leftmargini}{0em}
%  \origdescription
%  \setlength{\itemindent}{1em}
%}


\begin{document}

\maketitle \clearpage
\tableofcontents \clearpage

\begin{flushleft}
    \chapter{Introduction}
        \section{Read short introduction on Werewolf the Forsaken}
       
         
\section{The packs}
\subsection{PC pack : Night howlers}
Lynn Ethwings :  Teacher (Cahalith)\\
Peter Torhes : Cherif Chief (Elodoth)\\
Luke Hereford : Car fixer-Farmer (Rahu)\\
Leonard J. Andrews : Forest Guard (Irraka)\\
Jessica  Ethwings: Veterinary physician (Ithaeur)\\

\subsection{ The good guys : Sadness Knives}
Floria Centerfold : The black Eclipse (Alpha, Rahu, Hunter in darkness)\\
David McClurgan:  Red Fangs (Irraka, Hunter in darkness)\\
Helen Hallister : Vicious Pain (Cahalith, Blood talon)\\
Marshall Hereford : Fair Wolf ( Elodothe, Iron Master)\\
Morris Kenneth : Pointed Mind (Ithaeur, Bone Shadow)\\

\subsection{Bad guys : hidden claws}
Paul Debian : Winter Mist (Alpha, former member of the sadness Knives, Bale hound)\\
Clara Haltway : Forest’s Warth (Irraka, Hunter in darkness)\\
Casey Jones : Unwise Wolf (two fingers on his left hand are missing, ithaeur, Bone shadow)\\
Garry Oakman : Running Nightmare (Rahu, Blood talon)\\

\clearpage
\section{Cahalith}
\begin{description}
\item[Name:]{Lynn Ethwings}
\item[Origin:]{Canada}
\item[Auspice:]{Cahalith}
\item[Tribe:]{Blood Talon}
\item[Job:]{Teacher}
\item[Age:]{24}
\item[Biography:]{ 
 You are a young woman and a little bit shy. you come from a rich family. You have followed Art and Literature studies in several universities across the world: North America, Europe, Asia. 
You like to paint, and your painting became noticed really quickly. Your painting represents your dreams. They describe dark places with creepy shapes.\\ 
At that time, your older sister (Jessica) gets really crazy. She vanished completely.\\
You did not really care about it. You had a life to live. You leaved in New-York city. One week before your first exposition in a famous gallery, your sister shows up to you.\\
She asks you to stop making those painting. She said : "Your paintings show things that must be hidden". You did not understand why and you told her to own her own business. On the exposition opening eve, you surprise her destroying your artworks. This woke up a huge anger in you.
The next days, you were in your apartment and your sister had empty the fridge.\\ 
With a large smile, she explained that you become a werewolf. Then, you left NYC to find other members for your pack.
You demonstrate some abilities to localize person about to experience their first change. 
Your sister made this pack. At the end, you land in a small Canadian village. You became teacher at the primary school.\\
Recently, your dreams show a downpour, many dead wolves and an owl asking for help. 
The weirdest thing, this morning you woke up in your class room. You don't remember anything about last night. 
Those brain meltdowns last longer and occur more frequently. \\
Avis:\\
\underline{Peter Torhes} : Good guy but he has some black folder. One day, his past will explode, and it will hurt you all.\\
\underline{Luke Hereford} : Kind guy, he is the biggest pack weapon. He is fascinating, he has absolutely no culture at all, but he is not borried of it.\\
\underline{Leonard J. Andrews} : Lonely guy, he wants to make everything alone. That may leads him to troubles. Really dedicated guy to his job and to his pack.\\
\underline{Jessica  Ethwings}: your sister, she is the alpha of the pack, the main part. She is a good alpha, but a bad sister. \\
}
\end{description}
\clearpage
\textbf{\large Dons} 
\vspace{0.5cm}

\don{The good words}{+2 en social passif}{}{}{117}
\don{Cri de ralliemment}{}{Manipulation + Expression + Gloire}{1 Volonté}{119}
\don{Canaliser la rage}{}{Vigeur + Survie + Pureté}{1 point d'essence}{142}

\clearpage
\section{Rahu}
\begin{description}
\item[Name:]{Luke Hereford}
\item[Origin:]{}
\item[Auspice:]{Rahu/Guerrier}
\item[Tribe:]{Iron Master}
\item[Job:]{Garagiste / Agriculteur}
\item[Deed Name:]{}
\item[Age:]{22 years}
\item[Biography:]{
Son of a single mother, you have lived in. Your mother did many jobs: waitress, cleaning... \\
Your father is dead before you birth. Your mother was very angry about him.\\
When you was 15-old, your mother became sick. she's got Leukemia. You did whatever you can to save her. 
But without health insurance, the health care was to expensive. Your help was useful but not enough.
When she died, you found help into alcohol. One day, you receive a letter, which said that you are grand parent are dead and you are in their legacy. 
You get a little ranch in the small village in Canada. You fixed the house and start an activity of fixing cars. You also received few fields and a small cow herd. 



Dans le village, tu as ouvert ton garage. Tu répares les engins agricoles ou les voitures. Tes affaires marchent pas trop mal. Lors d'une balade 
sur tes terres pour sélectionner des arbres, tu as été mordu par un loup. Bizarrement, tu n'as pas ressenti une énorme douleur. 
La nuit suivante, quatre personnes (deux hommes et deux femmes) sont entrées chez toi. Ils t'ont retenu en otage et t'ont parlé de divers éléments pour t'énerver. 
Visiblement ils connaissaient bien des choses sur toi.  Quand ils ont évoqué ta mère, cela n'a pas loupé, tu t'es énervé. Eux aussi. Tu te 
souviens vouloir les défoncer. Visiblement, ça c'est pas passé ainsi. 
Ils se sont excusés mais c'était la seule façon pour eux de te réveiller. Ils t'ont expliqué que tu était un loup-garou. La meute s'est 
installée dans ton village.
Tu as de bonnes relations avec les habitants, et surtout tu les connais depuis 4 ans maintenant.\\

Avis:\\
\underline{Peter Torhes} : Il est marrant, il semble avoir un passé assez lourd, mais qui n'en a pas ? Puis, c'est un bon partenaire d'entrainement. \\
\underline{Lynn Ethwings }: Très sympa, elle te casse un peu les pieds avec sa culture des villes. Elle devrait garder les pieds sur terre.\\
\underline{Leonard J. Andrews} : Il est de bon conseil, un peu trop concentrer dans son travail (meute ou humain)\\
\underline{Jessica Ethwings}: Tu espères sincèrement ne jamais la décevoir. Elle te fait un peu peur. C'est une bonne Alpha.\\
}
\end{description}
\clearpage
\textbf{\large Dons} 
\vspace{0.5cm}


\don{Redresser}{}{}{1 Point d'Essence}{125}
\don{Nuit Noire}{coupe la lumière }{Astuce + Larcin + Ruse}{1 volonté}{146}
\don{Clarté}{+ 5 en init}{}{1 Point d'Essence}{137-136}

\clearpage
\section{Irraka}
\begin{description}
\item[Name:]{Leonard J. Andrews}
\item[Origin:]{USA}
\item[Auspice:]{Irraka}
\item[Tribe:]{Hunter in darkness}
\item[Job:]{National Park Guardian }
\item[Age:]{19 years}
\item[Biography:]{
You are a young bully and outlaw. Social services have taken you to different places during your childhood.
You never knew your parents\\ 
Your bad actions drive you to jail For teenagers. 
You escaped several times to get 

Tu as réussi à t'échapper plusieurs fois pour passer quelques nuits à la belle étoile. 
Le cadeau après ce genre de fugue, c'est un bon passage à tabac en règle. \\
Même ces avertissements ne t'empêcheraient pas d'y retourner. \\
Les coups étaient de plus en plus puissant te lançant parfois quelques jours dans le coma. 
C'est là que tu as compris qu'il fallait fuir pour de bon. Tu t'es donc enfui de la prison. 
Tu as été blessé pendant l'opération. Tu as fui dans la forêt en espérant trouver un refuge, dans une grotte que tu avais déjà repéré.
Tu as entendu s'approcher les gardiens à ta recherche, ils sont rentrés dans ta grotte, tu as hurlé "Cassez vous !". 
Bizarrement, ils l'ont fait. Tu as pu lire de la peur sur leur visage. \\
Le matin suivant, tu t'es réveillé dans l'arrière d'une voiture. À l'avant, deux filles : Jessica et Lynn Ethwings. Elles t'ont pris en charge, nourri. 
Elles ont fait annuler les charges contre toi (aux vues des mauvais traitements). Tu as compris que tu étais un loup-garou. Vous avez fait un bout de chemin ensemble. \\
Sur place, tu es devenu garde-chasse, officier des eaux et forêt. Tu surveilles une  partie d'un parc naturel. \\ 
Depuis quelques mois, tu fréquentes Elisabeth Lecoeur, une éducatrice venu du Québec. 
Avis:\\
\underline{Peter Torhes} : Un filou, assez sympa mais traine de grosses valises, un jour cela vous pètera à la gueule.\\
\underline{Luke Hereford} : Simple bonhomme, il est la force de frappe de la meute. Un peu trop cavalier à ton goût, il ne prend pas assez de recul sur les évènements.\\
\underline{Lynn Ethwings}  : Ses rêves sont une vraie bénédiction pour la meute. Pourtant, elle semble porter le deuil de sa nouvelle nature, tu crains qu'elle soit trop faible pour assurer son devoir envers la meute.\\
\underline{Jessica  Ethwings}: Tu l'admires, elle dégage un vrai charisme, tu serais prêt à la suivre n'importe où.\\
}
\end{description}
\clearpage
\textbf{\large Dons} 
\vspace{0.5cm}

\don{Communion avec la forêt}{}{Manipulation + Survie + Ruse}{1 point d'essence}{130-131}
\don{Pieds de Brûme}{}{}{1 point d'essence}{114}
\don{Diriger le feu}{}{Force + Survie + Gloire}{1 point d'essence}{109}

\clearpage
\section{Elodothe}
\begin{description}
\item[Nom:]{Peter Torhes}
\item[Origine:]{Chicago}
\item[Auspice:]{Elodothe/juge}
\item[Tribu:]{Storm Lord}
\item[Profession:]{Chérif}
\item[Liste de dons]:
\item[Age:]{35 ans}
\item[Histoire:]{
Tu étais un avocat d'affaires de Chicago. 
Tu faisais du bon travail et tu as plongé la tête baissée dans le monde de la nuit de Chicago.
Tu sais maintenant que Chicago est aux mains de créatures surnaturelles. 
Tu leur as laissé une assez mauvaise impression. \\
Ils n'ont pas beaucoup l'habitude que les repas se défendent.
Tu as tué le bras droit du prince, pendant ton premier changement. \\
C'est après cet évènement que tu as rencontré les sœurs Ethwings. 
Elles t'ont accueilli dans leur meute, camouflé tes bêtises. \\
En bouquet final, tu as volé beaucoup d'argent au crime de Chicago. 
Ce petit village canadien est un endroit parfait. \\
Tu es devenu le chérif de la ville. Ton boulot est très administratif, mais tu peux faire un peu comme tu veux niveau horaire. 
Au sein de la meute, tu passes pour le vilain petit canard, tu aimerais prouver le contraire. \\

Avis:\\
\underline{Lynn  Ethwings} : fille coincée, dans son monde, elle te snoble clairement.\\
\underline{Luke Hereford} : Un jeune qui a de la suite dans l'idée, tu es un peu jaloux.\\
\underline{Leonard J. Andrews} : Il se tuera au travail. Il devrait profiter plus des joies de la vie.\\
\underline{Jessica  Ethwings}: très surprenante, elle est ton seul vrai soutien dans la meute. \\
}
\end{description}
\clearpage
\textbf{\large Dons} 
\vspace{0.5cm}

\don{Changement partiel}{}{Vigueur + Survie + Instinct primal}{[1 point de volonté]}{121}
\don{Voix autoritaire}{}{ Manipulation + Intimidation + Honneur vs Résolution + calme}{1 Point d'Essence}{107}
\don{Aura de trêves}{}{Manipulation + Persuation + Honneur}{1 Point d'Essence}{113}


\clearpage
\section{Ithaeur}
\begin{description}
\item[Nom:]{Jessica Ethwings}
\item[Origine:]{Canada}
\item[Auspice:]{Ithaeur/Shaman}
\item[Tribu:]{Bone Shadow}
\item[Profession:]{Vétérinaire}
\item[Age:]{26 ans}
\item[Histoire:]{ 
Pendant tes études, tu as subi ta première transformation après avoir surpris ton mec avec une copine à toi. Tu les as tués tous les deux.
La meute locale s'est chargé d'étouffer l'affaire (plus exactement de la faire bruler).\\
Ils t'ont appris ce qu'était les loups-garous. Poussée par une envie de comprendre, tu as enquêté sur ta famille pour y voir quelques irrégularités: des personnes manquantes...\\
Tes voyages ont permis de rencontrer d'autres loups-garous.\\
Tu as compris que la meute d'accueil n'était pas vraiment honnête avec toi. La réalité fut révélée par la suite: c'était des purs.
Après ta période crise d'identité, tu as décidé de reprendre contact avec ta soeur. Il est possible qu'elle ait un rôle à jouer.
En effet, tu l'as retrouvé une semaine avec le début de son exposition dans une galerie New-Yorkaise.\\
Tu lui as demandé de ne pas faire cette exposition. Ces peintures représentaient clairement le monde des esprits.\\
Tu avais peur que tes ennemis l'attaquent. Pour la protéger, tu as détruit ses oeuvres. Tu n'avais jamais vu en colère à ce point.
Elle s'est transformée et vous vous êtes battues. Elle a bien faillit te tuer, ton expérience t'a sauvé. Le lendemain, tu lui as tout expliqué.
Vous êtes parties ensuite à la recherche d'un territoire et de nouveaux frères de meute.\\
Finalement vous êtes arrivés dans le petit village de Springfield au Canada.  \\
Avis:\\
\underline{Peter Torhes} : Il sait lire les gens et n'est pas le dernier dans les combats. Cependant son besoin de richesse et de gloire pourrait un jour lui être dangereux pour la meute. \\
\underline{Luke Hereford} : Petit dernier de la meute. Il te semble encore trop inconscient des dangers qui vous entourent.\\
\underline{Leonard J. Andrews} : Toujours fidèle au poste. Tu as une bonne amitié avec lui.\\
\underline{Lynn Ethwings}: Ta sœur, tu dois la protéger. Elle est trop fragile pour ce monde. Elle t'a bien aidé pour trouver des camarades de meute. Tu sais bien qu'elle prend sa nature comme un fléau.\\
}
\end{description}
\clearpage
\textbf{\large Dons} 
\vspace{0.5cm}

\don{Langue animale}{}{Manipulation + Animaux + Pureté}{1 point de volonté}{130}
\don{Sentir la malice}{}{Astuce + Occulte + Sagesse}{}{114}
\don{Témoignage de cadavre}{}{Manipulation + Occulte + Pureté}{1 point d'essence}{129}

\chapter{The story}
\section{What the characters know}
\begin{itemize}
\item Lynn Ethwings :  institutrice (Cahalithe) : Beaucoup d'enfant sont absent. 
\item Peter Torhes :  Chérif (Elodothe) : Vision du conte le petit chaperon rouge, sauf qu'a la fin une femme pleure le loup. 
\item Luke Hereford : agriculteur (Rahu) : Animaux mort 
\item Leonard J. Andrews : garde chasse (Irraka) : un Sénateur US et sa famille sont dans le coin. Cela demande un petit plus en sécurité. Ils souhaitent faire des chasses bien importante. 
\item Jessica  Ethwings: vétérinaire (Ithaeur) : 
\end{itemize}
\section{Environment}
\section{Hisil}
The spirit of the zone have been traumatized by a event, before the pack set up there. In game that means -3 dices to any social rolls with spirits.
As you can see on the territory map, the forbidden zone is hold by a powerful forest spirit. The spirit (rank 9) has whatched the pack for more than 1 year (since the pack's arrival). He decides to test them by asking then to perform the Holy Hunt rite. So he sends a fow spirit as his ambassador and prey for the rite. 


\section{The holy hunt}
Saterday's night, the pack must perform the holy Hunt rite. RedTail arrives to the pack locus in the forest. The rite must take place into the hisil. 
RedTail has the side of a normal fox, but he always keeps a huge smile and his front legs are really big and sinewy. 
So, Jessica should roll dices to perform the rite (I don't respect strictly the rules because by the rules, jessica can't make this rite).

RedTail starts to run in the deep forest (to the north). the pack wait and then start to chase RedTail. Redtail's smell ends up under huge dead tree's roots. Only one urhan character can follow the track down there. The character looks up and see, RedTail laughing in the empty tree trunk.  Redtail goes out really quickly by running on a branch and jump away of the pack. The pack starts chasing him. Let's them think they can catch him. I like to use the chasing rule. RedTail has 10 success in advance and has a speed of 23. After two or three turn of chasing, Redtail jumps above a hole and hide himself in the forest. The hole is in reality a brook and it required 3 success at Strengh+Althletic to jump it without fall in the water. 
But when every character has passed the brook spirit, they all feel that the rite is broken.  


\section{Monster under the bed}
The pack will try to understand what is wrong and they may seek RedTail. It is scared to death under a stone. It can't speak. But all the spirit around are in the same state. It's easy to figure out that the trouble zone shapes a line to the village. They can follow the track of fear. Several yards away, they find a spirit very powerful (rank 10). It looks like fire but fire of black flames, a carpet of black flames. \\

It is really difficult to go close to him (resolve + composure - malus). As they are going closer as the malus grows. I used to start at -1 for 20 meters, -4 for 10 meters and -8 for 5 meters (I never used this one). Its power is passive, the active ones are really painful (take Nightmare discipline from Nosferatu clan as reference, if you need inspiration and rules). When the first member experiences the death rage to escape the place, they stopped to go closer.  
Lynn has no need to do the roll, the spirit wants to speak to her.\\

Let's your players speak with the spirit. It will tell them that its presence on their territory is the evidence of their incompetence. They should make their job in a better way. It will thank Lynn (secretly and she will gain a gift allowing her to freeze somebody (see fearstruck numin in Predators).
You players must understand that this spirit is attracted to (the essence of) the village. The spirit creeps slowly to the village and it will be there at the morning.

\section{Meanwhile in the village}
\subsection{Physical World}
Every thing seems normal, streets are empty and quiet. But spending time to watch allows witnesses to figure out a pattern in houses. The light turns on at the first floor for 20 minutes and turns off. In fact, children have fear crisis, so parent try to calm them, then they go back to sleep. Players must talk to parent for understanding that. 

\subsection{Hisil side}
In the village, things start to be really fucked up. Wounds start to appear in houses (in children bed rooms). They are small but if all wounds grows up they will make a big one.
It is really sudden. 

\section{Investigations}
The investigation won't lead to something useful. The ritual is over so the character must get some sleep because tomorrow they must attend to the "Divine Service".

\section{Dead Owl}
Peter Torhes will find a crucified owl on his door. It was alive and It dies due to the leak of blood. 
There are footprint and wheelprint in the mud, but the player has to look for them.

\section{Divine Service} 
The whole village used to come at the Divine Service. It is the best opportunity to show off. Our characters have important role in the village: teacher, policeman (candidate to the mayor election), forest guard and Veterinary physician. 
The first thing that players can noticed is about the mayor. He is well-dressed with a really expensive suit. Usually, he was dressed like a redneck/farmer. 
There is less people than expected. There are no children under 12 year-old and one parent stays at home to take care of them. 
To get those information: Wits + empathy. 
The mayor invites everyone for picnic and barbecue just after the divine service. Actually it is his first campaign meeting. 

\section{A storm is coming}
the two sides kicks of Peter come to inform the mayor and Peter about a big storm coming on the village.  The rain will start in few hours.  At 8 pm, it will be the start of the worst part of the storm and it 
will last until 2a.m. Leonard is also informed by this young assistant : a teenager who help him after high school. 
The mayor takes a speaker and informs the population attending the meeting, that they should prepare their house to the storm. Peter's assistants take cars to inform the whole village. 
After this announcement, everyone looks scared and they leave the barbecue.
It is a good idea to the PC to do so. Elisabeth asks help to her boyfriend (Leonard). 

\section{Hidden claws are calling you}
When they all work on the house. They will heard (or feel) the call of remote werewolf. 
The message cannot be translated in words but the feeling gives the idea of appointment.
It's coming from the East of the Night howlers' territory (about 70km). 
So they can take a car or something to meet these werewolves. They meet the Hidden claws pack at the border of their territory. 
The Hidden claws alpha warms the player about Thomas centerfold. He is a former member of the Hidden claws pack, but he became a Zi'ir (crazy werewolf, harmony 0). The Hidden claws has followed his trace for a while and he may be somewhere in the Night howlers' territory. 
Winter Mist also tells them to kill him if they found him. He is really dangerous and completely out of control, he changed in urshul and gouru form before many humans. 
He also kills many people and feed on them. \\ 
One Hidden claws members shows his hand, and 2 fingers are missing. He got the injury fighting Thomas: "He ate my fingers".
Hidden claws has informed the Night howlers pack because they don't want to hunt on Night howlers' territory.  \\
Note: in reality this pack are the bad guys, so it is important to role-play them as nice people, really concerned about the fate of Thomas and really friendly with your players. \\
They looks like veteran and good warriors (far better than the players' pack). \\






\section{While the storm}
Players come back to the village under the rain. Jessica must make a Dexterity + drive roll if she drives her bike. 
Elisabeth Lecoeur asks help to her boyfriend (Leonard). He can feel that she is really scared.
During the storm, he is strongly recommended to stay at home, even for werewolves. If they try to get out, make them feel pain. 
Anyways, they will hear the howl of wolf pack in the forest. 

\section{End of the Storm}
About 1 a.m, the storm is gone and it is possible to reach out. 
The player will probably check out the wolves they heard few hour ago. 
The forest has changed a bit. Many trees are down and Leonard has to make a Wits + survival to find a usable path. 

 
Des cadavres de plusieurs loups sont retrouvés mort dans la forêt du parc naturel. 
Ils semblent y avoir eu un combat. Un loup blessé s'est fait encerclé par une meute. La meute attend comme affamée. 
Puis passe à l'attaque, le blessé semble se préparé à subir l'attaque. La victime s'est transformé en forme Gouru et a massacré quelques loups.
La rage mortelle de l'individu peut troublé l'esprit ou la personne qui voit la scene. [ résolution + calme ] si un PJ voit la scene par un don l'image devient noire, l'esprit à eu peur, il a "fermé les yeux". 
Musique : Foret 

\section{Les sadness knives}
Le jeu est de montrer les tensions entre cette meute qui débarque (qui a possédé ce territoire) et les PJ qui ont pris leur place.
La meute protège et cherche Thomas Centerfold. Ils s'opposeront à l'intervention de la meute des joueurs.


\section{Tempete: les conséquences}
Les plus gros dégats sont enregistrés chez la famille: Porkman. Ils ont des triplés. Les enfants jouaient dans la grange, quand elle s'est effrondrait, 
ils ont eut le temps de partir dans la maison, qui s'est effrondré à son tour. Ils se sont réfugiés dnas la dépendance en brique de la maison.

\section{Les enfants}
 Les enfants témoigneront de “il est revenu le monstre”. Il peuvent aussi parler de l’animatrice de la Mairie, qui raconte plein de contes et le chauffeur du bus scolaire.

\section{Floria}
Floria jurera avoir senti l’odeur de son fils(elle ne fait pas très saine d’esprit). Sa meute n’y croit pas trop.

\section{Peur dans la forêt}
Il est possible de trouver un loup plein de cailloux. Il a était sauvagement opéré. cela peut être les parents d'un enfant. 

\section{Les Loups dans la ville}
Des meutes de loups semble de plus en plus s'approcher des humains dans la foret. esprit du carnage du conte de fée. 
Il est difficile de prouver leur existance. 


\section{Raison de la présence du Grand méchant loup}
Il y a principalement trois raisons de sa présence: 
\begin{itemize}
\item Floria Centerfold: Inspecte les maisons pour y chercher son fils, souvent en forme de loup. 
\item Thomas Centerfold: Est dans la zone, il souffre d'un rituels. Un ongle d'argent sous la peau le rend fou de douleur.
\item Elisabeth Lecoeur: La monitrice de la mairie, elle est du quebec. Elle Raconte des contes aux enfants, elle est infuencé par l'esprit de la peur.
\item Le tableau dans la salle de cours de Lynn. 
\item Vanille Street : un père torture ses enfants. 
\item Le maire est possédé par un esprit de la ville. Chicago veut se vanger
\item Un meute de Loup s'engardit 
\end{itemize}
Les vents soufflent, ils me guident en ce lieu. 

\end{flushleft}
\end{document}
